### 2015-11-21 README.Rmd
phylomatic fxns made defunct, changes throughout pkg, bumepd dev version

<tbody>
<tr>
	<td style="text-align:left;">Encylopedia of Life</td>
	<td style="text-align:left;"><code>eol</code></td>
	<td style="text-align:left;"><a href="http://www.eol.org/api/">link</a></td>
	<td style="text-align:left;"><a href="http://eol.org/users/register">link</a></td>
</tr>
<tr>
	<td style="text-align:left;">Taxonomic Name Resolution Service</td>
	<td style="text-align:left;"><code>tnrs</code></td>
	<td style="text-align:left;">"api.phylotastic.org/tnrs"</td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">Integrated Taxonomic Information Service</td>
	<td style="text-align:left;"><code>itis</code></td>
	<td style="text-align:left;"><a href="http://www.itis.gov/ws_description.html">link</a></td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">Phylomatic</td>
	<td style="text-align:left;"><code>phylomatic</code></td>
	<td style="text-align:left;"><a href="http://phylodiversity.net/phylomatic/html/documentation.html">link</a></td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">Global Names Resolver</td>
	<td style="text-align:left;"><code>gnr</code></td>
	<td style="text-align:left;"><a href="http://resolver.globalnames.org/api">link</a></td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">Global Names Index</td>
	<td style="text-align:left;"><code>gni</code></td>
	<td style="text-align:left;"><a href="https://github.com/dimus/gni/wiki/api">link</a></td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">IUCN Red List</td>
	<td style="text-align:left;"><code>iucn</code></td>
	<td style="text-align:left;"><a href="https://www.assembla.com/spaces/sis/wiki/Red_List_API?version=3">link</a></td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">Tropicos</td>
	<td style="text-align:left;"><code>tp</code></td>
	<td style="text-align:left;"><a href="http://services.tropicos.org/help">link</a></td>
	<td style="text-align:left;"><a href="http://services.tropicos.org/help?requestkey">link</a></td>
</tr>
<tr>
	<td style="text-align:left;">Theplantlist dot org</td>
	<td style="text-align:left;"><code>tpl</code></td>
	<td style="text-align:left;">**</td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">Catalogue of Life</td>
	<td style="text-align:left;"><code>col</code></td>
	<td style="text-align:left;"><a href="http://www.catalogueoflife.org/colwebsite/content/web-services">link</a></td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">Global Invasive Species Database</td>
	<td style="text-align:left;"><code>gisd</code></td>
	<td style="text-align:left;">***</td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">National Center for Biotechnology Information</td>
	<td style="text-align:left;"><code>ncbi</code></td>
	<td style="text-align:left;">none</td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">CANADENSYS Vascan name search API</td>
	<td style="text-align:left;"><code>vascan</code></td>
	<td style="text-align:left;"><a href="http://data.canadensys.net/vascan/api">link</a></td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">International Plant Names Index (IPNI)</td>
	<td style="text-align:left;"><code>ipni</code></td>
	<td style="text-align:left;"><a href="http://www.ipni.org/link_to_ipni.html">link</a></td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">Barcode of Life Data Systems (BOLD)</td>
	<td style="text-align:left;"><code>bold</code></td>
	<td style="text-align:left;"><a href="http://www.boldsystems.org/index.php/Resources">link</a></td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">National Biodiversity Network (UK)</td>
	<td style="text-align:left;"><code>nbn</code></td>
	<td style="text-align:left;"><a href="https://data.nbn.org.uk/Documentation/Web_Services/Web_Services-REST/resources/restapi/rest.html">link</a></td>
	<td style="text-align:left;">none</td>
</tr>
</tbody>
</table>

>>>>

<tbody>
<tr>
	<td style="text-align:left;">Encylopedia of Life</td>
	<td style="text-align:left;"><code>eol</code></td>
	<td style="text-align:left;"><a href="http://www.eol.org/api/">link</a></td>
	<td style="text-align:left;"><a href="http://eol.org/users/register">link</a></td>
</tr>
<tr>
	<td style="text-align:left;">Taxonomic Name Resolution Service</td>
	<td style="text-align:left;"><code>tnrs</code></td>
	<td style="text-align:left;">"api.phylotastic.org/tnrs"</td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">Integrated Taxonomic Information Service</td>
	<td style="text-align:left;"><code>itis</code></td>
	<td style="text-align:left;"><a href="http://www.itis.gov/ws_description.html">link</a></td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">Global Names Resolver</td>
	<td style="text-align:left;"><code>gnr</code></td>
	<td style="text-align:left;"><a href="http://resolver.globalnames.org/api">link</a></td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">Global Names Index</td>
	<td style="text-align:left;"><code>gni</code></td>
	<td style="text-align:left;"><a href="https://github.com/dimus/gni/wiki/api">link</a></td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">IUCN Red List</td>
	<td style="text-align:left;"><code>iucn</code></td>
	<td style="text-align:left;"><a href="https://www.assembla.com/spaces/sis/wiki/Red_List_API?version=3">link</a></td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">Tropicos</td>
	<td style="text-align:left;"><code>tp</code></td>
	<td style="text-align:left;"><a href="http://services.tropicos.org/help">link</a></td>
	<td style="text-align:left;"><a href="http://services.tropicos.org/help?requestkey">link</a></td>
</tr>
<tr>
	<td style="text-align:left;">Theplantlist dot org</td>
	<td style="text-align:left;"><code>tpl</code></td>
	<td style="text-align:left;">**</td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">Catalogue of Life</td>
	<td style="text-align:left;"><code>col</code></td>
	<td style="text-align:left;"><a href="http://www.catalogueoflife.org/colwebsite/content/web-services">link</a></td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">National Center for Biotechnology Information</td>
	<td style="text-align:left;"><code>ncbi</code></td>
	<td style="text-align:left;">none</td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">CANADENSYS Vascan name search API</td>
	<td style="text-align:left;"><code>vascan</code></td>
	<td style="text-align:left;"><a href="http://data.canadensys.net/vascan/api">link</a></td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">International Plant Names Index (IPNI)</td>
	<td style="text-align:left;"><code>ipni</code></td>
	<td style="text-align:left;"><a href="http://www.ipni.org/link_to_ipni.html">link</a></td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">Barcode of Life Data Systems (BOLD)</td>
	<td style="text-align:left;"><code>bold</code></td>
	<td style="text-align:left;"><a href="http://www.boldsystems.org/index.php/Resources">link</a></td>
	<td style="text-align:left;">none</td>
</tr>
<tr>
	<td style="text-align:left;">National Biodiversity Network (UK)</td>
	<td style="text-align:left;"><code>nbn</code></td>
	<td style="text-align:left;"><a href="https://data.nbn.org.uk/Documentation/Web_Services/Web_Services-REST/resources/restapi/rest.html">link</a></td>
	<td style="text-align:left;">none</td>
</tr>
</tbody>
</table>
